Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-01 doc/manuscript/manuscript.Rmd
update locus table

```{r , echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
loc_table %>%
  mutate(allele = round(allele, 2)) %>%
  mutate(Repeats = case_when(
    Repeats <= 2 ~ "di-",
    Repeats <= 3 ~ "tri-",
    Repeats <= 4 ~ "tetra-",
    Repeats <= 5 ~ "penta-",
    Repeats <= 6 ~ "hexa-"
  )) %>%
  rename(`*h*` = Hexp) %>%
  rename(`No. alleles` = allele) %>%
  rename(`Repeat Motif` = Repeats) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 3:4, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 5:6, 2) %>%
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.11, 0.1, 0.05, 0.075)) %>%
  huxtable::print_md(max_width = 61)
```

>>>>

```{r , echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
#    Locus    Range Repeats allele      Hexp  Evenness
#  1   5-2 318--324 2.00000      4 0.4522344 0.6164147
#  2   6-2 483--495 5.99999      3 0.6445842 0.9493734
#  3   7-2 158--174 2.00000      7 0.7290665 0.7635293
#  4   8-3 244--270 2.00000      7 0.7418669 0.7892240
#  5   9-2 360--382 2.00000      9 0.3475110 0.4055573
#  6  12-2 214--222 2.00000      5 0.5804776 0.7791017
#  7  17-3 342--363 3.00000      7 0.5527510 0.5264941
#  8  20-3 280--282 2.00000      2 0.0532974 0.4204995
#  9  55-4 153--216 4.00000     10 0.7231380 0.6564025
# 10 110-4 370--386 3.99999      5 0.7555955 0.9147773
# 11 114-4 339--416 4.00000     10 0.8306310 0.8012051

loc_table %>%
  mutate(allele = round(allele, 2)) %>%
  mutate(Repeats = case_when(
    Locus == "5-2"   ~ "(GT)",
    Locus == "6-2"   ~ "(TTTTTC)(TTTTTG)(TTTTTC)", # "(TTTTTC)~2~(TTTTTG)~2~(TTTTTC)",
    Locus == "7-2"   ~ "(GA)",
    Locus == "8-3"   ~ "(CA)",
    Locus == "9-2"   ~ "(CA)(CT)", # "(CA)~9~(CT)~9~",
    Locus == "12-2"  ~ "(CA)",
    Locus == "17-3"  ~ "(TTA)",
    Locus == "20-3"  ~ "(GT)GG(GT)", # "(GT)~7~GG(GT)~5~",
    Locus == "55-4"  ~ "(TACA)",
    Locus == "110-4" ~ "(TATG)",
    Locus == "114-4" ~ "(TAGA)"
  )) %>%
  rename(`*h*` = Hexp) %>%
  rename(`No. alleles` = allele) %>%
  rename(`Repeat Motif` = Repeats) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 3:4, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 5:6, 2) %>%
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.25, 0.1, 0.05, 0.075)) %>%
  huxtable::print_md(max_width = 90)
```
